Human Factors Influencing Visual Statistical Inference

### 2013-06-14 sociology_paper.tex
subjectwise learning trend added

\begin {abstract}  
Visual statistical inference is a way to determine significance of patterns found while exploring data. It is dependent on the evaluation of a lineup, of a data plot among a sample of null plots, by human observers. Each individual is different in their cognitive psychology and judiciousness, which can affect the visual inference. The usual way to estimate the effectiveness of a statistical test is its power. The estimate of power of a lineup can be controlled by combining evaluations from multiple observers. Factors that may also affect the power of visual inference are the observers' demographics, visual skills, and experience, the sample of null plots taken from the null distribution, the position of the data plot in the lineup, and the signal strength in the data. This paper examine these factors. Results from multiple visual inference studies using Amazon's Mechanical Turk are examined to provide an assessment of these. The experiments suggest that individual skills vary substantially,  but demographics do not have a huge effect. There is evidence that a learning effect exists that observers get faster with repeated evaluations which suggests a potential for using the lineup protocol for training people to read statistical graphics. The placement of data plot in the lineup does not affect the inference.

@@

\subsection{Data Collection Methods}  Human observers were recruited to evaluate the experimental lineups through Amazon Mechanical Turk \cite{turk} or MTurk Web site.  It is an online work place where people from around the world can perform some tasks and get paid. Usually tasks are very simple and no specialized training is required. Being a human is the main requirement. Tasks are designed for anyone to do but some tasks may require that workers satisfy some skill level depending on the recruiters need. The tasks are designed such that it does not take much time to complete. Humans are still better than computers in performing these types of tasks. The the amount of money paid for each task is very small as well.

It is very fast, cheap and reliable to recruit people from MTurk. Thats why it is getting very popular among the researchers who perform human subject experiment. The another benefit is that a very diverse pool of subjects can be recruited which is otherwise very hard to obtain for a study. The researchers can easily filter the workers based on their experimental design, such as recruiting people only from a specific geographical location or a group of people who satisfy certain criteria etc. The recruiter can decide who they pay or not. Workers have to satisfy the task requirement to ensure payment. But at the end it is the recruiter who has the final say. Usually recruiters pay promptly after the task has been done properly and thats why MTurk is very popular among the online job seeker. At any point of time thousands of tasks are available for the thousands of workers around the world.

Because of its convenience it is getting popular for scientific research study as well. In comparison with a lab study \cite{suri:2010} perform the same study using MTurk and demonstrate that their study results are as good as the lab study results even though MTurk study required less time and cost while provided more convenience. \cite{majumder:2013} recruited people from MTurk for their simulation study in estimating the power of visual statistical inference. They have done numerous pilot studies in lab before doing actual MTurk study and found similar results. \cite{mason:2012} explains various features of MTurk and describes how it can be used as part of human behavioral study.

We designed and developed a web site which enables to display the lineups to the observers as per experimental design. The MTurk workers were redirected to the web site and the data were collected, stored automatically into a local database server. Demographic informations such as age group, gender and education levels were also collected. The time taken for each evaluation is computed based on the time the plot was shown and the time the feedback was received. The location of the observer is determined by the ip address of the observer.

\subsection{Model to Estimate Demographic Factor Effect} Suppose $Y_{ij}$ denotes the response from observer $i$ on a  lineup $j$. Let $\pi_{ij}=  E(Y_{ij})$ be the probability that  observer $i$ correctly picks the data panel from lineup $j$. We model this in a generalized mixed effects model of the form
\begin{equation} \label{eqn:demographic_response}
g( \pi_{ij} )= \mu + X_{i}\beta + \ell_j,  
\end{equation}

where $\mu$ is an overall average probability for picking out the data plot from a lineup. $X_{i}=(X_{1i},X_{2i}, .., X_{pi})'$ is the vector of demographic factors of the observer $i$ and $\beta$ is the corresponding fixed effect coefficient vector. $p$ indicates the number of demographic factor variables. For $\ell_j$ we assume a normal distribution, $N(0, \sigma_\ell^2)$. $\ell_j$ is a random intercept predicting lineup difficulty level. $g(.)$ denotes the {\it logit} link function $g(\pi)=g_1(\pi)=\log(\pi) - \log(1-\pi); 0 \le \pi \le 1$.

@@

The feedback provided by each observer on a lineup is a binary response variable. Suppose $Y_{ijk}$ denotes the response from observer $i$ on a  lineup $j$ in his/her $k$th attempt.  $Y_{ijk}=1$ if the response is correct otherwise  $Y_{ijk}=0$.

%As per the design of the experiment for learning trend we have two different response variables. One is observer feedback on a lineup which is a binary variable.  The other variable is the time taken for each evaluation which is a continuous variable. Suppose random variable $Y_{\ell, i}$ denotes the response from subject $ i=1,2, ..., I$ on lineup $\ell=1,2, ..., L$. We model the mean $\mu_{\ell, i} = E(Y_{\ell, i})$ with a generalized liner mixed effect model
%
%\begin{equation} \label{eqn:trend}
%g( \mu_{\ell, i} )= W_{\ell i} \delta +  Z_{\ell i}  \tau_{\ell i},  
%\end{equation}

%\hh{
Let $\pi_{ijk}=  E(Y_{ijk})$ be the probability that  observer $i$ correctly picks the data panel from lineup $j$ in his/her $k$th attempt. We model this in a generalized mixed effects model of the form
\begin{equation} \label{eqn:trend_response}
g( \pi_{ijk} )= \mu + \alpha_k + u_i +  a_{i} k + \ell_j,  
\end{equation}
where $\mu$ is an overall average probability for picking out the data plot from a lineup, $\alpha_k$ is the effect of the $k$th attempt on the probability, with $\alpha_1 = 0$ and $k = 1, ..., K$.
$u_i$ and $a_i$ are observer specific random effects, $i = 1, ..., I$. $u_i$ is a random intercept, describing a basic subject-specific ability. We assume $u_i \sim N(0, \sigma_u^2)$. 
$a_i$ is a random slope capturing an individuals' specific learning effect over the course of $K$ attempts. We assume $a_i \sim N(0, \sigma_a^2)$. 
For $\ell_j$ we again assume a normal distribution, $N(0, \sigma_\ell^2)$. $\ell_j$ is a random intercept predicting lineup difficulty level. $g(.)$ denotes the {\it logit} link function $g(\pi)=g_1(\pi)=\log(\pi) - \log(1-\pi); 0 \le \pi \le 1$ .

@@

@@

Since the actual data plot is same for each of the null sets of plot, the response data constitutes a multivariate response. Thus, to examine if the difference in proportion correct among the locations is statistically significant we fit a one way multi variate analysis of variance (MANOVA) model to the data.

@@

\subsection{Overview of the Data} Figure \ref{fig:turker_location} displays the location around the world from where a total of 2321 participants provided feedback data on the lineups in all the ten experimental studies. Even though most of the participants were from the United States and India, we have participants from 76 different countries. This provides a diverse pool of participants in terms of geographical locations. The diversity in not only in geographical locations of the participants but also in their gender, age groups and education levels as we see in Table \ref{tbl:demographics}.  It is interesting that the number of male and female participants are almost same even though there are lot of people from developing countries.

@@

Male and female participants are similarly distributed among all age groups except age 18-25 in India where less female participants were observed as we see in Figure \ref{fig:gender_country_bar}. The distribution of education levels are also different across the countries for this age group. Most of the participants from India are below age 40 while in United States the distribution of participants are similar beyond age 40.

A total of 1911 lineups were evaluated in all these 10 experiments. Each person was supposed to evaluate 10 lineups except experiment 9 where three lineups were evaluated by each person. To clean the data we used the test plot as the basis and did not include the results of that test plot. In some cases the demographic information were not provided by the participants. Also, for some ip address, the actual geographical locations could not be retrieved. This resulted some missing demographic information.

\subsection{Demographic Factors} Proportions of correct responses and the logarithm of average time taken to evaluate  each lineup are computed and their distributions are shown as boxplots in Figure \ref{fig:demographic_effect} for different demographic factor levels. Averages of these distributions are represented by dots inside the boxplots. The youngest age group (18-25) took least average time to evaluate a lineup. People from India took more time than others. People who have only a high school degree took less time and this is related to what we have seen for young age group. The time taken by male and female participants are almost similar. None of the factors are significant in describing time taken to evaluate a lineup.

@@

We observed some variations in median proportion of correct responses for different levels of the demographic factors as in Figure \ref{fig:demographic_effect}. But the variability of proportion correct responses are huge as per design of the experiments since we have some easy and some difficult lineups. There were lineups which were not expected to be evaluated correctly and some were very easy and expected to be evaluated correctly 100\% of the time. This is why we see the boxes ranges from 0 to 1 in most of the factor levels.

Unlike median, less variations are observed in the averages for different factor levels. As expected, there is no significant difference between Male and female performances. Among all the demographic factor levels only graduate degree, India and age group 31-35 appear to be significantly different from others. Most of the Indian participants reported to have a graduate degree. Thus the effect of graduate degree is actually the effect of India.

\subsection{Learning Trend} Models \eqref{eqn:trend_response} and \eqref{eqn:trend_time} are fitted to the data from experiment 5, 6, and 7 separately. For this the function $lmer()$ is used from R package $lme4$ by \cite{lme4:2011}. To obtain the $p$-values of fixed effect parameters estimates, normal approximation is used for $Z$ scores computed as the ratio of estimates to the estimated standard errors.

Table \ref{tbl:model_result_response} presents the parameter estimates and $p$-values of fixed effect estimates of Model \eqref{eqn:trend_response}. The larger $p$-values suggest that none of the levels of attempt ($\alpha_2$ through $\alpha_{10}$) appears to be significant at \%1 significance level. Moreover, some of the estimates are positive and some are negative and they show up seemingly in random order suggesting later attempts not necessarily improved. This indicates that there may be no learning effect on the proportion of correct evaluations.

@@

@@

%\begin{table}[ht]
%\centering
%\begin{tabular}{rrrlllrrll}
%  \hline
% & Est & SE & Zval & pvalue & g1 & Est & SE & Zval & pvalue \\ 
%  \hline
%(Intercept) & 3.465 & 0.014 & 241.52 & $<$0.001 &   & -0.834 & 0.073 & -11.43 & $<$0.001 \\ 
%  age_level26-30 & 0.058 & 0.013 & 4.5 & $<$0.001 &   & 0.062 & 0.049 & 1.27 & 0.2058 \\ 
%  age_level31-35 & 0.068 & 0.014 & 4.72 & $<$0.001 &   & 0.115 & 0.055 & 2.08 & 0.0375 \\ 
%  age_level36-40 & 0.231 & 0.016 & 14.05 & $<$0.001 &   & 0.310 & 0.063 & 4.93 & $<$0.001 \\ 
%  age_level41-45 & 0.176 & 0.021 & 8.56 & $<$0.001 &   & 0.158 & 0.081 & 1.96 & 0.0501 \\ 
%  age_level46-50 & 0.272 & 0.024 & 11.29 & $<$0.001 &   & 0.141 & 0.096 & 1.47 & 0.1425 \\ 
%  age_levelabove 50 & 0.352 & 0.018 & 19.19 & $<$0.001 &   & 0.147 & 0.071 & 2.06 & 0.0394 \\ 
%  countryRest of the world & -0.086 & 0.016 & -5.52 & $<$0.001 &   & 0.267 & 0.060 & 4.49 & $<$0.001 \\ 
%  countryUnited States & -0.230 & 0.012 & -19.39 & $<$0.001 &   & 0.186 & 0.046 & 4.05 & 1e-04 \\ 
%  degree.L & 0.042 & 0.013 & 3.25 & 0.0011 &   & -0.083 & 0.050 & -1.65 & 0.098 \\ 
%  degree.Q & -0.037 & 0.012 & -3.21 & 0.0013 &   & -0.044 & 0.045 & -0.97 & 0.3306 \\ 
%  degree.C & 0.117 & 0.013 & 9.12 & $<$0.001 &   & 0.070 & 0.050 & 1.42 & 0.1566 \\ 
%  degree^4 & 0.046 & 0.011 & 4.12 & $<$0.001 &   & 0.182 & 0.043 & 4.22 & $<$0.001 \\ 
%  gender_levelMale & 0.078 & 0.009 & 8.26 & $<$0.001 &   & 0.055 & 0.036 & 1.5 & 0.1329 \\ 
%  pic_name (Intercept) & 0.082 & 0.287 &  &  &   & 5.259 & 2.293 &  &  \\ 
%   \hline
%\end{tabular}
%\end{table}

@@

\begin{figure}[htbp] 
   \centering
   \includegraphics[width=6.5in]{learning_trend.pdf} 
   \caption{ Mean residuals of proportion correct obtained from the model \eqref{eqn:trend_response} fitted without attempt are plotted against attempt. Linear regression lines fitted through the points are shown. None of the slopes in these three experiments are statistically significant.}
   \label{fig:learning_trend_response}
\end{figure}

@@

\begin{figure}[htbp] 
   \centering
   \includegraphics[width=6.5in]{learning_trend_time.pdf}    
%   \includegraphics[width=6.5in]{learning_trend_time_subject.pdf}    
   \caption{ Mean residuals of log(time taken) obtained from model \eqref{eqn:trend_time} fitted without covariate attempt plotted against attempt. Linear regression lines are fitted through the points excluding the first attempt. For all the three experiments the downward slopes are statistically significant which indicates that MTurk workers take less time as they progress through their attempts.}
   \label{fig:learning_trend_time}
\end{figure}

@@

Observer demographics don't seem to have significant influence on performance in time taken to evaluate a lineup. Some variation is observed in terms of median proportion correct, but the overall average proportion of correct responses over different demographic factors levels seem to be similar.

With simulation experiments, it is observed that the performance of human observers does not increase through successive attempts while evaluating multiple lineups. But their skill in evaluating the lineup in shorter time gets improved over successive evaluations. When an observer evaluates multiple lineups, the earlier evaluations take significantly longer than the later evaluations. This result is very important as it suggests that the power estimated for visual inference using human subject experiment is robust and may not change if those participants are allowed to give feedback again. This investigation suggest that the skilled person may only do it faster.

@@

\clearpage
\section{Electoral Building Lineups and Results}
Figures~\ref{fig:elect-1} and \ref{fig:elect.2} through~\ref{fig:elect.5} are the five lineups shown to (different) Amazon Turk workers in an experiment. They all are created as described in the introduction of the paper. In order to not bias observers, no context information was given about how these plots were created or what data they were displaying. This also made it necessary to slightly more stylize the display.

@@

\begin{figure}[htbp] 
   \centering
   \includegraphics[width=0.8\linewidth]{electoral-2-17.pdf} 
   \caption{Lineup \#2 - electoral building. Which building looks the most different from the other buildings? }
   \label{fig:elect.2}
\end{figure}
\begin{figure}[htbp] 
   \centering
   \includegraphics[width=0.8\linewidth]{electoral-3-18.pdf} 
   \caption{Lineup \#3 - electoral building. Which building looks the most different from the other buildings? }
   \label{fig:elect.3}
\end{figure}
\begin{figure}[htbp] 
   \centering
   \includegraphics[width=0.8\linewidth]{electoral-4-17.pdf} 
   \caption{Lineup \#4 - electoral building. Which building looks the most different from the other buildings? }
   \label{fig:elect.4}
\end{figure}
\begin{figure}[htbp] 
   \centering
   \includegraphics[width=0.8\linewidth]{electoral-1-1.pdf} 
   \caption{Lineup \#5 - electoral building. Which building looks the most different from the other buildings? }
   \label{fig:elect.5}
\end{figure}

>>>>

\begin {abstract}  
Visual statistical inference is a way to determine significance of patterns found while exploring data. It is dependent on the evaluation of a lineup, of a data plot among a sample of null plots, by human observers. Each individual is different in their cognitive psychology and judiciousness, which can affect the visual inference. The usual way to estimate the effectiveness of a statistical test is its power. The estimate of power of a lineup can be controlled by combining evaluations from multiple observers. Factors that may also affect the power of visual inference are the observers' demographics, visual skills, and experience, the sample of null plots taken from the null distribution, the position of the data plot in the lineup, and the signal strength in the data. This paper examine these factors. Results from multiple visual inference studies using Amazon's Mechanical Turk are examined to provide an assessment of these. The experiments suggest that individual skills vary substantially,  but demographics do not have a huge effect on performance. There is evidence that a learning effect exists that observers get faster with repeated evaluations which suggests a potential for using the lineup protocol for training people to read statistical graphics. The placement of data plot in the lineup does not affect the inference.

@@

\subsection{Data Collection Methods}  Human observers were recruited to evaluate the experimental lineups through Amazon Mechanical Turk \citep{turk} or MTurk Web site.  It is an online work place where people from around the world can perform some tasks and get paid. Usually tasks are very simple and no specialized training is required to do them. Being a human is the main requirement. Tasks are designed for anyone to do but some tasks may require that workers satisfy some skill level depending on the recruiters need. Each task is usually planned to complete in a short time. Humans are still better than computers in performing these types of tasks. The the amount of money paid for each task is very small as well.

%It is very fast, cheap and reliable to recruit people from MTurk. Thats why it is getting very popular among the researchers who perform human subject experiment. The another benefit is that a very diverse pool of subjects can be recruited which is otherwise very hard to obtain for a study. The researchers can easily filter the workers based on their experimental design, such as recruiting people only from a specific geographical location or a group of people who satisfy certain criteria etc. The recruiter can decide who they pay or not. Workers have to satisfy the task requirement to ensure payment. But at the end it is the recruiter who has the final say. Usually recruiters pay promptly after the task has been done properly and thats why MTurk is very popular among the online job seeker. At any point of time thousands of tasks are available for the thousands of workers around the world.

%Because of its convenience it is getting popular for scientific research study as well. In comparison with a lab study \cite{suri:2010} perform the same study using MTurk and demonstrate that their study results are as good as the lab study results even though MTurk study required less time and cost while provided more convenience. \cite{majumder:2013} recruited people from MTurk for their simulation study in estimating the power of visual statistical inference. They have done numerous pilot studies in lab before doing actual MTurk study and found similar results. \cite{mason:2012} explains various features of MTurk and describes how it can be used as part of human behavioral study.

We designed and developed a web application which enables to display the lineups to the observers as per experimental design. The MTurk workers were redirected to the web site and the data were collected, stored automatically into a local database server. Demographic informations such as age group, gender and education levels were also collected. The time taken for each evaluation is computed based on the time the plot was shown and the time the feedback was received. The location of the observer is determined by the ip address of the observer.

\subsection{Model to Estimate Demographic Factor Effect} The feedback provided by each observer on a lineup is a binary response variable. Suppose $Y_{ij}$ denotes the response from observer $i$ on a  lineup $j$. Yij = 1 if the response is correct otherwise Yij = 0. Let $\pi_{ij}=  E(Y_{ij})$ be the probability that  observer $i$ correctly picks the data panel from lineup $j$. We model this in a generalized mixed effects model of the form
\begin{equation} \label{eqn:demographic_response}
g( \pi_{ij} )= \mu + X_{i}\beta + \ell_j,  
\end{equation}
where $\mu$ is an overall average probability for picking out the data plot from a lineup. $X_{i}=(X_{1i},X_{2i}, .., X_{pi})'$ is the vector of demographic factors of the observer $i$ and $\beta$ is the corresponding fixed effect coefficient vector. $p$ indicates the number of demographic factor variables. For $\ell_j$ we assume a normal distribution, $N(0, \sigma_\ell^2)$. $\ell_j$ is a random intercept predicting lineup difficulty level. $g(.)$ denotes the {\it logit} link function $g(\pi)=g_1(\pi)=\log(\pi) - \log(1-\pi); 0 \le \pi \le 1$.

@@

Multiple lineups were sequentially shown to each observer for evaluation. Suppose $Y_{ijk}$ denotes the response from observer $i$ on a  lineup $j$ in his/her $k$th attempt.  $Y_{ijk}=1$ if the response is correct otherwise  $Y_{ijk}=0$. Let $\pi_{ijk}=  E(Y_{ijk})$ be the probability that  observer $i$ correctly picks the data panel from lineup $j$ in his/her $k$th attempt. We model this in a generalized mixed effects model of the form
\begin{equation} \label{eqn:trend_response}
g( \pi_{ijk} )= \mu + \alpha_k + u_i +  a_{i} k + \ell_j,  
\end{equation}
where $\mu$ is an overall average probability for picking out the data plot from a lineup, $\alpha_k$ is the effect of the $k$th attempt on the probability, with $\alpha_1 = 0$ and $k = 1, ..., K$.
$u_i$ and $a_i$ are observer specific random effects, $i = 1, ..., I$. $u_i$ is a random intercept, describing a basic subject-specific ability. We assume $u_i \sim N(0, \sigma_u^2)$. 
$a_i$ is a random slope capturing an individuals' specific learning effect over the course of $K$ attempts. We assume $a_i \sim N(0, \sigma_a^2)$. 
For $\ell_j$ we again assume a normal distribution, $N(0, \sigma_\ell^2)$. $\ell_j$ is a random intercept predicting lineup difficulty level. $g(.)$ denotes the {\it logit} link function $g(\pi)=g_1(\pi)=\log(\pi) - \log(1-\pi); 0 \le \pi \le 1$ .

@@

To fit all these mixed effect models the function $lmer()$ is used from R package $lme4$ by \cite{lme4:2011}. To obtain the $p$-values of fixed effect parameters estimates, normal approximation is used for $Z$ scores computed as the ratio of estimates to the estimated standard errors.

@@

As per the design of experiment for location effect, the actual data plot is same for each of the null sets of plot. Thus the response data of this experiment constitute a multivariate response. To examine if the difference in proportion correct among the locations is statistically significant we fit a one way multi variate analysis of variance (MANOVA) model to the data.

@@

\subsection{Overview of the Data} Figure \ref{fig:turker_location} displays the location around the world from where a total of 2321 participants provided feedback data on the lineups in all the ten experimental studies. Even though most of the participants were from the United States and India, we have participants from 76 other different countries. This provides a diverse pool of participants in terms of geographical locations. The diversity in not only in geographical locations of the participants but also in their gender, age groups and education levels as we see in Table \ref{tbl:demographics}.  It is interesting that there were large number of female participants even though there were lot of people from developing countries.

@@

Male and female participants are similarly distributed among all age groups except age 18-25 in India where less female participants were observed as we see in Figure \ref{fig:gender_country_bar}. The distribution of education levels are also different across the countries for this age group. Most of the participants from India are below age 40 while in United States the distribution of participants are similar beyond age 40. There were not many participants beyond age 50 and hence these age groups are merged to form one age group called above 50. In exploratory analysis and model fitting this new age group is used instead of actual age groups beyond age 50.

A total of 1911 lineups were evaluated in all these 10 experiments. Each person was supposed to evaluate 10 lineups except experiment 9 where three lineups were evaluated by each person. A test plot was shown to each observer and the feedback received from that plot is used to examine the data quality. But the data received for the test lineup is not included in the analysis. In some cases the demographic information were not provided by the participants. Also, for some ip address, the actual geographical locations could not be retrieved. This resulted some missing demographic information.

\subsection{Demographic Factors} Proportions of correct responses and the logarithm of average time taken to evaluate  each lineup are computed and their distributions are shown as boxplots in Figure \ref{fig:demographic_effect} for different demographic factor levels. Averages of these distributions are represented by dots inside the boxplots. The youngest age group (18-25) took least average time to evaluate a lineup. People from India took more time than others. People who have only a high school degree took less time and this is related to what we have seen for young age group. The time taken by male and female participants are almost similar.

%All of the factors are significant in describing time taken to evaluate a lineup.

@@

The distribution of time taken to evaluate a lineup is positively skewed. But in log scale it is symmetric for all the demographic factor variables as we see in Figure \ref{fig:demographic_effect}. Mean and medians are very similar as well. This allowed us to fit linear mixed model to the log time taken with normal error structure.

We observed some differences in median proportion of correct responses for different levels of the demographic factors as in Figure \ref{fig:demographic_effect}. But the variability of proportion correct responses are huge as per design of the experiments since we have some super easy and some extremely difficult lineups. There were lineups which were not expected to be evaluated correctly since some of the null plots in those lineups were showing more signal than the actual plot itself. In those scenarios,  one may not reject the null hypothesis. We call these difficult lineup. Some of the lineups were so easy that data plot is detectable in a first glance. These were expected to be evaluated correctly 100\% of the time. This is why we see the boxes range from 0 to 1 in most of the factor levels. Unlike median, less differences are observed in the average proportion of correct responses for different factor levels.

Model \eqref{eqn:demographic_response} is fitted to the data for different demographic factors such as age, country, education and gender. The results are shown in Table \ref{tbl:model_result_demographics}. For parameter estimation the first factor levels shown the Table are are used as the base line. The age group 36-40 is significantly different than the base line age group 18-25. The rest of the age levels appears to be similar in explaining the probability of correct response. For country, the rest of the world is different from USA but India appears to be similar to USA. We see from Table \ref{tbl:demographics} that most of the participants (about 90\%) are from India and USA. The rest of the 10\% data are from 76 different countries. This diversity in the rest of the world may make it different from India and USA.

@@

The graduate degree holders are significantly different as well. The positive parameter estimate indicates that they perform better and the probability of correct response is higher than other education levels. As expected, there is no significant difference between Male and female performances.

Notice that lineup specific variance estimate is 5.259 with a standard error of 2.293 which is much higher than the other significant parameter estimates in Model \eqref{eqn:demographic_response}. This indicates that the major and most important factor affecting the probability of correct response is the lineup difficulty. This is also evident from the large variability in the proportion correct in Figure~\ref{fig:demographic_effect}. Because of this huge impact of lineup specific variance, the actual effect of other factor variables on the probability of correct response is in fact very small even though they appear to be significant.

Model \eqref{eqn:demographic_time} is fitted for the log time taken to evaluate a lineup and the results are also shown in  Table~\ref{tbl:model_result_demographics}.  The effect of all the demographic factors on log time taken to evaluate a lineup appears to be significant.

@@

\subsection{Learning Trend} Models \eqref{eqn:trend_response} and \eqref{eqn:trend_time} are fitted to the data from experiment 5, 6, and 7 separately. Table \ref{tbl:model_result_response} presents the parameter estimates and $p$-values of fixed effect estimates of Model \eqref{eqn:trend_response}. The larger $p$-values suggest that none of the levels of attempt ($\alpha_2$ through $\alpha_{10}$) appears to be significant at \%1 significance level. Moreover, some of the estimates are positive and some are negative and they show up seemingly in random order suggesting later attempts not necessarily improved. This indicates that there may be no learning effect on the probability of correct evaluations.

@@

\begin{figure}[htbp] 
   \centering
   \includegraphics[width=6.5in]{learning_trend.pdf} 
    \includegraphics[width=6.5in]{learning_trend_subject.pdf} 
   \caption{ Mean residuals of proportion correct obtained from the model \eqref{eqn:trend_response} fitted without attempt are plotted against attempt. Linear regression lines fitted through the points are shown. None of the slopes in these three experiments are statistically significant.}
   \label{fig:learning_trend_response}
\end{figure}

@@

\begin{figure}[htbp] 
   \centering
   \includegraphics[width=6.5in]{learning_trend_time.pdf}    
 \includegraphics[width=6.5in]{learning_trend_time_subject.pdf}    
   \caption{ Mean residuals of log(time taken) obtained from model \eqref{eqn:trend_time} fitted without covariate attempt plotted against attempt. Linear regression lines are fitted through the points excluding the first attempt. For all the three experiments the downward slopes are statistically significant which indicates that MTurk workers take less time as they progress through their attempts.}
   \label{fig:learning_trend_time}
\end{figure}

@@

Observer demographics seem to have significant influence on performance in time taken to evaluate a lineup. Some variation is observed in terms of probability of correct evaluation. Age group 36-40, Countries other than India and United states, People who have a graduate degree appear to have significantly more probability to evaluate a lineup correctly. Gender does not have any effect on performance.

Individual learning trend is observed in both time taken and observer performance. But the overall performance of human observers does not increase through successive attempts while evaluating multiple lineups. The skill in evaluating the lineup in shorter time gets improved over successive evaluations. The earlier evaluations take significantly longer than the later evaluations. This result is very important as it suggests that the power estimated for visual inference using human subject experiment is robust and may not change if those participants are allowed to give feedback again. This investigation suggest that the skilled person may only do it faster.

@@

\clearpage
\section{Electoral Building Lineups and Results}
%Figures~\ref{fig:elect-1} and \ref{fig:elect.2} through~\ref{fig:elect.5}

Five lineups were shown to (different) Amazon Turk workers in an experiment. They all were created as described in the introduction of the paper. In order to not bias observers, no context information was given about how these plots were created or what data they were displaying. This also made it necessary to slightly more stylize the display.

@@

%\begin{figure}[htbp] 
%   \centering
%   \includegraphics[width=0.8\linewidth]{electoral-2-17.pdf} 
%   \caption{Lineup \#2 - electoral building. Which building looks the most different from the other buildings? }
%   \label{fig:elect.2}
%\end{figure}
%\begin{figure}[htbp] 
%   \centering
%   \includegraphics[width=0.8\linewidth]{electoral-3-18.pdf} 
%   \caption{Lineup \#3 - electoral building. Which building looks the most different from the other buildings? }
%   \label{fig:elect.3}
%\end{figure}
%\begin{figure}[htbp] 
%   \centering
%   \includegraphics[width=0.8\linewidth]{electoral-4-17.pdf} 
%   \caption{Lineup \#4 - electoral building. Which building looks the most different from the other buildings? }
%   \label{fig:elect.4}
%\end{figure}
%\begin{figure}[htbp] 
%   \centering
%   \includegraphics[width=0.8\linewidth]{electoral-1-1.pdf} 
%   \caption{Lineup \#5 - electoral building. Which building looks the most different from the other buildings? }
%   \label{fig:elect.5}
%\end{figure}
